Master's Project Journal

### 2019-03-09 tex_files/Journal.tex
jurnal

\end{document}

>>>>

\section*{Twas the week before the midterm}
This week was eventful but frustrating. I did not manage to make progress on any goals per say, but I discovered what was the cause behind the inverse locking that I had been seeing sometimes. Turns out it was being caused by the phase detector design which I was using being stable for very small gains and a small number of bit phase detection and if the falling edge of signal 1 toggled back and forth between rising on signal two I would get oscillation between positive and negative, or lead and lag to use the correct terms, and with the tiny gains making it actually stable in this state. Changing the detector to a more conventional style that did not terminate a measurement until the next rising edge on the opposite signal fixed this probem. The new issue now is that I cannot get low jitter locking, seeingly down to the behaviour of the loop filter.\\
The loop filter appears to work correctly when the two paths are taken in isolation but when combining the paths it breaks down. Either through being too aggressive and doesnt lock or from the ki value being too small, and when it is too small the output of the loop filter toggles between a value of min and maxval thus creating a huge amount of jitter.
\end{document}
